Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-12-10 thesis.Rmd
Första word verion - ska fixa lite i de nya tabellerna

---
title: "Opportunities for improvement in the care of adult trauma patients arriving in shock"
subtitle: "Add a Subtitle if Needed"
author: "Carl Skog"
output:
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_file = "thesis") })
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Opportunities for improvement in the care of adult trauma patients arriving in shock"
subtitle: "Add a Subtitle if Needed"
author: "Carl Skog"
output:
  #html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_file = "thesis") })
editor_options: 
  markdown: 
    wrap: 72
---
